e8_analysis

### 2015-09-21 analysis/e8_analysis.Rmd
added norming section - do we take care of this in RSA??? Next step to plot the literal semantics

qplot(scalars, y=cnt,
      geom="bar", stat="identity",
      data=dc) +
  facet_wrap(~degree)
qplot(scalars, y=hi,
      geom="bar", stat="identity", main="low", ylim=c(0, 150),
      data=data.frame(overall.cnts))

```

>>>>

qplot(scalars, y=cnt,
      geom="bar", stat="identity",
      data=dc) +
  facet_wrap(~degree)
qplot(scalars, y=hi,
      geom="bar", stat="identity", main="low", ylim=c(0, 150),
      data=data.frame(overall.cnts))
```

```{r}
# working with vector
normed.counts = NA
s = scalars[1]
d = dgrs[2]

for (s in scalars) {
  cnts = data.frame()
  for (d in dgrs) {
    cnts$scale = rep(s, 5)
    cnts$dgrs = rep(d, 5)
    cnts = ms[ms$scale == s & ms$degree == d, "cnt.judgment"] + 1       # Laplace smooth
    cnts = cnts / sum(cnts)
  }
  new.sems = c(new.sems, cnts)
}
as.vector(unlist(new.sems))
ms

# init.df
# ------
# initialze a new nrows * ncols data.frame()
init.df = function(ncols, nrows, names = NA) {
  new.df = data.frame(matrix(ncol = ncols, nrow = nrows))
  colnames(new.df) = names
  return(new.df)
}

# working wit df()
new.sems = data.frame(scale=character(),
                      degree=character(),
                      stars=numeric(),
                      cnt.judgment=numeric())
for (s in scalars) {
  cnts = init.df(4, 5, names=c("scale", "degree", "stars", "cnt.judgment"))
  for (d in dgrs) {
    cnts$scale = rep(s, 5)
    cnts$degree = rep(d, 5)
    cnts$stars = seq(1, 5)
    cnts$cnt.judgment = ms[ms$scale == s & ms$degree == d, ]$cnt.judgment + 1 # Laplace smooth
    cnts$cnt.judgment = cnts$cnt.judgment / sum(cnts$cnt.judgment)
    new.sems = rbind(new.sems, cnts)
  }
}
# for merging with ms df()
new.sems = rbind(new.sems, data.frame(scale=rep("training1", 5),
                           degree=c(rep("hi",5), rep("low",5)),
                           cnt.judgment=rep(NA,10)))
ma = merge(ms, new.sems, by=c("scale", "degree", "stars"))
```
